
<!-- No YAML front matter! -->
<!-- SINGPLE items must have the following form: -->
<!-- number followed by a full stop stem wording {[week][difficulty]}, -->
<!-- wehre difficulty is one of S - simple, E - easy, M - moderate, D - difficult -->

<!-- Stem can have multiple lines but the {} tag must be at the end of the first line with no full stop after it. -->

<!-- Code chunks are allowed -->

<!-- Response options are denoted using leading "- " -->
<!-- No full stops after response options. -->
<!-- Correct answer should be denoted with " (correct)" -->

<!-- All valid markdown allowed including maths mode, e.g., $\bar{x}$ -->

01. What is the name of the package you are learning to use? {02E}

Items may contain a lead in line like this but question tag must be on the FIRST line.

```{r}
#code chunks are allowed
```

- `teachR` (correct)
- `tidyverse`
- `base`
- `rcanvas`

02. Items can be also just one-liners like this {02M}

- Bilbo (correct)
- Frodo
- Gndalf
- Elrond

<!-- QUESTION GROUPS -->
<!-- Items can share a single stem/paradigm -->
<!-- This must be denoted with [multi] at the beginning of the group -->
<!-- Group stems have NO NUMBER -->

[multi]Answer the following 3 questions with respect to the plot below.

```{r mv_scatter_print}
# if objects are called but not generated, the code to create them
# must be included in a separate Rmd file that gets passed to question.bank
mv_violin
```

{ <!-- after group stem, there must be an opening curly brace closed after the end of the group -->

38. What kind of plot is this? {04S}

- Violin plot (correct)
- Histogram
- Scatterplot
- Dotplot

39. As for the number of variables plotted, this plot is: {04E}

- Multivariate (correct)
- Univariate
- Bivariate
- Facetted

40. What kind of relationship does the plot show? {04M}

- Negative (correct)
- Positive
- Causal
- This kind of plot does not show relationships
} <!-- close group -->

<!-- Best to leave an empty last line -->
